# Lanin Training Report
## Training (Startup) Parameters
The training process was started at `r format(start.time, "%Y-%m-%d_%H-%M")`.

The startup Parameters are:
```{r, comment=NA}
opt
```

## Training and Validation Symbols
These Symbols were used for training:
```{r, comment=NA}
set1Syms
set2Syms
vdSyms
```

## Training Set Generation
### X
Input Variables: `r x.remark`

Example of raw data set:
```{r, comment=NA}
head(set1.RAW[[1]][complete.cases(set1.RAW[[1]])])
```

### Y
Output Variables: `r y.remark`

Boundaries:
```{r, comment=NA}
set1.adv.boundaries
set2.adv.boundaries
vd.adv.boundaries 

set1.dec.boundaries
set2.dec.boundaries
vd.dec.boundaries 
```

### Schema of Training Data Set
Example:
```{r, comment=NA}
head(trainDF1a.t)
```

## Training Algorithm
Training Algorithm: `r a.remark`

### train objects
required time:

```{r}
time.1a
time.2a
time.1d
time.2d
```

```{r, comment=NA, echo=FALSE}
for (i in 1:length(fit)) {
  cat(paste(names(fit)[i], ":\n"))
  print(fit[[i]])
  cat("-----------------------------------------------------------\n\n")
}
```

### Confusion Matrices
```{r, comment=NA, echo=FALSE}
for (i in 1:length(cm)) {
  cat(paste(names(cm)[i], ":\n"))
  print(cm[[i]])
  cat("-----------------------------------------------------------\n\n")
}
```

The script completed at `r format(Sys.time(), "%Y-%m-%d_%H-%M")`.